Tables and Figures - Supplement A and B

### 2019-12-11 code/06_Supplement-tables-figures.Rmd
Supplement C reported as a correlation matrix instead of figure

#Table S1.
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

>>>>

#Table S1A.
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

## Supplement C

```{r, preprocessing}

SMDs_raw <- dat %>% filter(outcomes1_2 == "mean _ SD") %>% 
  mutate(wi = compute_precision(SD1 = outcome_t2, SD2 = outcome_c2, n1 = ntreatment, n2 = ncontrol)) #compute_precision function is sourced

average_within <- SMDs_raw %>% #these values we now wish to correlate with meta-analytic results
  group_by(effect) %>% 
  summarize(s2 = sum(wi) * (n()-1) / (sum(wi)^2 - sum(wi^2))) %>% #Average within study variance; equation 9. Higgins and Thompson (2002). n() = k [number of studies in a meta-analysis]
  ungroup()

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced

tau_per_type <- MD_standardized %>% 
  left_join(average_within) %>%
  mutate(sigma = sqrt(s2),
         eff_size = abs(eff_size),
         tau = sqrt(tau2)) #needed for bootfitter function below to work but not used

#As above but dropping the 4 largest effect sizes (Anchoring effects)----
without_anchoring <- tau_per_type %>% 
  filter(!grepl("Anchoring", effect))

corr_data <- tau_per_type %>%
  select(s2, eff_size, s_I2, H2) %>% 
  rename("$\\hat{\\mu}$" = "eff_size", "$I^2$" = "s_I2", "$H^2$" = "H2", "$s^2$" = s2)

corr_data_no_anchoring <- without_anchoring %>%
  select(s2, eff_size, s_I2, H2) %>% 
  rename("$\\hat{\\mu}$" = "eff_size", "$I^2$" = "s_I2", "$H^2$" = "H2", "$s^2$" = s2)

Table S1C. The Pearson correlations from 40 meta-analyses estimated with the random effects model and restricted maximum likelihood. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.

```{r, corr-table}

cors <- round(cor(corr_data), digits = 2)
cors[upper.tri(cors)] <- "" #make upper triangle empty in correlation matrix

knitr::kable(cors, booktabs = TRUE, escape = FALSE)
```

Table S2C. The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood. The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.

```{r, no-anchoring-corr}
cors_anch <- round(cor(corr_data_no_anchoring), digits = 2)
cors_anch[upper.tri(cors_anch)] <- "" #make upper triangle empty in correlation matrix

knitr::kable(cors_anch, booktabs = TRUE, escape = FALSE)
